### 2024-10-31 paper/2-background.tex
Add control structure

% structure
A WebAssembly program is comprised of \textit{modules}.
A module is the unit of deployment, loading, and compilation, which consists of
definitions such as functions, globals, and memories.
A module is instantiated to validate the module and allocate each definition to
the data structure named \textit{store}.
After the instantiation, functions can be invoked for the execution.

@@

% execution
WebAssembly execution is based on a stack machine.
An instruction consumes values in the stack as operands, produces the
resulting values, and pushes them to the stack.
\cref{fig:testop} is the WebAssembly specification for the \texttt{testop}
instruction.
Prose notation is written in the upper part, and formal notation is written in
the lower grey box.
In the prose notation, it pops a value from the stack, performs a test
operation, and pushes the result to the stack.
It is written compactly in the form of reduction rule in the formal notation
which consists of LHS, RHS, and premises: $(t.const ~ c_1) ~ t.testop$,
$(i32.const ~ c)$, and $c = testop_t(c_1)$.
The LHS means that when the value at the top of the stack $(t.const ~ c_1)$
and an instruction to execute is $t.testop$.
The RHS means that the value at the top of the stack is changed to $(i32.const
~ c)$, and this happens when the premise $c = testop_t(c_1)$ is satisfied.

% control flow

>>>>

% structure
A WebAssembly program is comprised of \textit{modules}.
A module is the unit of deployment, loading, and compilation, which consists of
definitions such as functions, globals, and memories.
A module is instantiated to validate the module, allocate each definition to
the data structure named \textit{store}.
This results in module instance, a runtime representation for the module.
After the instantiation, functions can be invoked for the execution.

@@

% execution
WebAssembly execution is based on a stack machine.
An instruction consumes values in the stack as operands, produces the
resulting values, and pushes them to the stack.
\cref{fig:testop} is the WebAssembly specification for the \texttt{testop}
instruction.
Prose notation is written in the upper part, and formal notation is written in
the lower grey box.
In the prose notation, it pops a value from the stack, performs a test
operation, and pushes the result to the stack.
It is written compactly in the form of reduction rule in the formal notation
which consists of LHS, RHS, and premises: $(t.const ~ c_1) ~ t.testop$,
$(i32.const ~ c)$, and $c = testop_t(c_1)$.
The LHS means that the value at the top of the stack is $(t.const ~ c_1)$,
and an instruction to execute is $t.testop$.
The RHS means that the value at the top of the stack is changed to $(i32.const
~ c)$, and this happens when the premise $c = testop_t(c_1)$ is satisfied.

% control structure
The stack stores not only the input and output values of the instructions but also
structures related to the control flow.
A \textit{call frame} and a \textit{label} are used for function call and
branching, respectively.
In exception handling proposal, there is a \textit{handler} for exception
handling, and other strucutres could be introduced in the future.
How these control structures are used for the control flow will be discussed in
\cref{sec:control flow in official prose}. \\
\red{TODO: remove dangling section header}
